Practical Machine Learning Course Project
========================================================
Author: Alecia Alianell
### Summary of Project
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

The data for the project is available here:
[Training](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv) 
[Test](https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv)

### Global Options
We will be using several libraries throughout the project, so they will be loaded here.
```{r,warning=FALSE}
require(caret)
require(rpart)
require(rpart.plot)
require(rattle)
require(randomForest)
```
#### Set Seed
Here we will set a seed so that the results are reproducible
```{r}
set.seed(1234)
```
#### Load Data and Partition into Datasets
We need to load the test and training datasets.  Also, based on the notes in class, 60% of the data is considered for the training dataset and remaining 40% is considered for the test dataset, whcih can be done using the classe variable.  We will also deal with the NA results in the datasets.
```{r}
traincsv <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv"
testcsv <- "http://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv"
train <- read.csv(url(traincsv), na.strings=c("NA","#DIV/0!",""))
test <- read.csv(url(testcsv), na.strings=c("NA","#DIV/0!",""))
inTrain <- createDataPartition(y=training$classe, p=0.6, list=FALSE)
Train.set <- training[inTrain, ]; Test.set <- training[-inTrain, ]
dim(train.set)
dim(test.set)
```
